XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler

### 2024-11-04 paper/main.tex
update paper

We address each of the above motivations and make the following main contributions:

\begin{enumerate}
  \item We designed a two stage pipeline, which we can employ a week LLM to extract target information. And a stronger LLM to program XPath.
  \item We proposed a simple way to prune the web page, which can reduce the complexity of the web page and make the LLM focus on the target information.
  \item We discovered a cue text that share context between two stage significantly improve the performance of the XPath programming agent.
  \item We benchmarked our approach against a state-of-the-art XPath programming agent across a suite of web crawling tasks. Our findings reveal that our approach excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
\end{enumerate}

>>>>

We based each of the above motivations and make the following contributions:

\begin{enumerate}
  \item We designed a two stage pipeline, which we can employ a weaker LLM to extract target information. And a stronger LLM to program XPath.
  \item We proposed a simple way to prune the web page, which can reduce the complexity of the web page and make the LLM focus on the target information.
  \item We discovered that extracted cue texts from 1st stage significantly improve the performance of the 2nd stage.
  \item We benchmarked our approach against a state-of-the-art same purpose agent across a suite of web crawling tasks. Our findings reveal that our approach excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
\end{enumerate}
